Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-19 paper/paper.tex
Add attachments correlations subsection to the paper

Attachments are, as mentioned previously, files attached to software tickets that can take any form - from code 
snippets written in Java to tar archives. We have analyzed all the high priority tickets

@@

>>>>

Attachments are, as mentioned previously, files attached to software tickets that can take any form - from code 
snippets written in Java to tar archives. We have analyzed all tickets that were both of high priority tickets and
were marked as Closed by the time we collected the data. Then we split all these tickets into two main categories: 
with attachments and without attachments. Furthermore, the tickets that were marked as having attachments were split 
into the categories specified in Section \ref{characterising}.

Using the plot package in our Go tool, we automatically generated the bar chart shown in Figure \ref{attachments}. 
As it can be seen, various types of attachments can produce completely different \emph{times-to-close}. For 
tickets with archive we can see the longest time-to-close mean while tickets having text attachments are at 
the other end of the spectrum. The smallest mean is for other attachments, which is represented by any file 
that does not have an extension specified in one of the other categories.

We assume that image attachments are screenshots attached to the ticket in order to help developers see and 
subsequently reproduce the bug. Thus, we can clearly see that the difference between the means of time-to-close 
for tickets without attachments and tickets with screenshots is significantly in favor of the latter. This can 
indicate that developers indeed find screenshots helpful in solving the ticket faster.

Another insightful result is the fact that having text, config and spreadsheet attachments significantly 
reduces the time-to-close for the ticket. This can imply that developers find value in various steps to reproduce, 
config values used by users when the bug encountered or data in a spreadsheet format (e.g. csv) that can be 
found in such files and helps them lower the time-to-close for the ticket.

On the other hand, having no attachments does not necessarily mean that the ticket will get closed after 
a longer period of time. As it can be seen in the figure, the mean time-to-close value for tickets without 
attachments is somewhat neutral in the entire data set.

A Welch T Test was computed to test the difference between tickets with attachments and those 
without attachments. The analysis revealed significant difference with $p > 0.01$ with an
average of $1380.551$ hours for tickets with attachments and an average of $3180.882$ hours
for tickets without attachments.

Thus, our analysis shows that having attachments in most formats, ranging from markdown files to PNG screenshots 
and snippets of code, can help developers solve the tickets faster. We believe that the solution of making attachments
provide the most value to the software project would be if issue tracking systems would make explicit to the reporters 
that uploading a screenshot or a code snippet can help reduce the time-to-close for the ticket.

@@

A Welch T Test was computed to test the difference between tickets with attachments (i.e. all categories 
shown in the graph and those without attachments. The analysis revealed significant difference with 
\emph{p} < 0.01 with an average of \emph{X <change this>} for tickets with attachments and an average of 
\emph{Y <change this>} for tickets without attachments.
